Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
comment
tightening

\vspace{1ex}
\noindent\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
previous sentence is correct.  I am just guessing by what you had earlier}.
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.
 Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, we focus on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

@@

\vspace{1ex}

\noindent\textbf{Question.}
Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. We are interested in understanding if
social factors, used as a proxy for experience, can be used to predict
a different success measure: commit integration success, therefore giving
developers and integrators another tool to be able to identify the quality
of a contribution performed by a particular developer.
%
Therefore our main research question, upon which we can build by investigating particular attributes, is:

@@

\vspace{1ex}
\noindent\textbf{Metric.} We measure quality software contributions by based on the build status of the
commit: if the build passes or fails.
To determine which factors are important for predicting build success, we used
a decision tree classifier~\cite{Quinlan86}, because decision tress are well a 
tested supervised classifier that are easy to interpret.
To explore the question of technical and social factors, we first build a
decision tree classifier using only the technical factors.  This first model
allowed us to understand how well commit complexity estimated build integration
success.  We then added the social factors to understand how the social factors
integrated with the technical factors when predicting build integration success.
We evaluated the predictive power of these two 
models with 10-fold cross validation.

@@

>>>>

\vspace{1ex}
\noindent\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
previous sentence is correct.  I am just guessing by what you had earlier}.
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.
 Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. By contrast, we focus on the relationship between independent social 
attributes and continuous integration success.

@@

\vspace{1ex}
\noindent\textbf{Question.}
%Previous studies have identified a relationship between technical and social 
%factors and pull request acceptance. 
We are interested in understanding whether
social factors, used as a proxy for experience, can be used to predict
a different success measure: commit integration success, therefore giving
developers and integrators another tool to be able to identify the quality
of a contribution performed by a particular developer.
%
Our main research question, upon which we can build by investigating particular attributes, is:

@@

\vspace{1ex}
\noindent\textbf{Metric.} We measure quality software contributions based on the build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to identify
important factors in predicting build success;  decision tress are well
established  and interpretable. 
We first build a
decision tree classifier using only technical factors, which highlights
the degree to which commit complexity predicts build integration
success.  We then added the social factors to identify the degree to which they
add predictive power to a the initial technical model. 
We use 10-fold cross validation across our evaluation.

@@

\todo{It is not acceptable to only use the shortened venue name.  Also, bilbiography entries are missing venues again; fix it.}
